---
title             : "Need for Cognition and Burnout in healthcare: The mediating role of self-control, emotion regulation, and coping strategies"
shorttitle        : "NFC and Burnout in healthcare"

author: 
  - name          : "Alexander Strobel"
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Writing - Original Draft"
      - "Writing - Review & Editing"
      - "Formal Analysis"
      - "Visualization"
      - "Data Curation"
      
  - name          : "Kea Rüter"
    affiliation   : "2"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Writing - Original Draft"
      - "Data Curation"
      - "Formal Analysis"

  - name          : "Anja Strobel"
    affiliation   : "2"
    corresponding : yes
    address       : "Technische Universität Chemnitz, Department of Psychology, Wilhelm-Raabe-Straße 43, 09120 Chemnitz, Germany"
    email         : "anja.strobel@psychologie.tu-chemnitz.de"
    role:
      - "Conceptualization"
      - "Writing - Review & Editing"
      - "Project Administration"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, Dresden, Germany"
  - id            : "2"
    institution   : "Department of Psychology, Technische Universität Chemnitz, Chemnitz, Germany"

authornote: |
  Alexander Strobel: https://orcid.org/0000-0002-9426-5397
  
  Anja Strobel: https://orcid.org/0000-0002-0313-0615 
   


abstract: |
  Burnout has emerged as a global health concern, with its prevalence notably increasing during the COVID-19 pandemic. 
  This especially occurs among individuals working within the field of healthcare. 
  In order to contribute to the improvement of working conditions and mental health, this study replicates a mediation model previously tested by Grass et al. [-@Grass-2018] among teaching students and by Zerna et al. [-@Zerna-2022] among teachers. 
  For this purpose, multiple mediation models, using a sample of N = 642 healthcare workers were examined. 
  The incorporated predictor was Need for Cognition (an intrinsic motivation to engage with cognitively demanding thoughts). 
  Mediators were self-control, the emotion regulation strategies reappraisal and suppression, as well as adaptive and maladaptive coping strategies. 
  The burnout subdimensions reduced personal efficiency, emotional exhaustion, and depersonalization each functioned individually as outcome variables. 
  In addition to the mediation analyses, correlation analyses of these variables were also calculated. 
  The results confirmed that adaptive coping strategies functioned preventively across all burnout dimensions. 
  Furthermore, reappraisal and maladaptive coping mediated the relationship between NFC and some subdimensions of burnout. 
  Healthcare workers who tended towards higher NFC appeared to be protected from burnout development due to various tested mediators. 
  Regarding the daily work environment, initial evidence suggests that efforts should be made to particularly promote adaptive coping strategies. 
  Future studies should further examine the link between NFC and burnout among healthcare professionals.
  
keywords          : "Need for Cognition, burnout, self-control, emotion regulation, coping"
wordcount         : "X"

bibliography      : 
  - "r-references.bib"
  - "NFC-Caregiver.bib"
floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
csl               : "apa7.csl"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("dplyr")   # for data manipulation 
library("here")    # for avoiding path edits
library("lavaan")  # for mediation analysis
library("papaja")  # for manuscript creation
library("psych")   # for descriptive statistics and correlation analysis
library("shape")   # for Arrows()

r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(242)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# locate relevant folder
here::i_am("flag_root_for_NFC-Caregiver.txt")
```

Burnout is a psychological, work-related stress syndrome and a global health concern [@Maslach-2003; @Parandeh-2022]. 
It correlates with depression [@Bianchi-2015], increased alcohol abuse [@Oreskovich-2012], and a heightened risk of suicidal thoughts [@Shanafelt-2011]. 
As a response to excessive work stress [@Maslach-1998], burnout affects not only individuals but also their workplace [@West-2018], leading to decreased productivity [@Dewa-2017], reduced job satisfaction, and intentions to leave the profession [@Shanafelt-2009].

Occupational stress is a growing problem, especially among healthcare workers [@Rink-2023]. <!-- was [@Hassan-2020], but very specific ref. (egypt healthcare workers) search for meta-analysis/review -->
Challenges like time constraints, lack of control, and competing demands are significant job strains (Lyndon, 2015). <!-- find better fitting ref. -->
The COVID-19 pandemic further exacerbated burnout rates [@Galanis-2021; @Prasad-2021]<!-- check ref. fit -->, as healthcare workers faced higher health risks, increased workloads, inadequate equipment, and limited resources.
These strains impacted not only the workers but also the quality of patient care, leading to lower patient satisfaction and increased medical errors [@West-2018].

The rising number of burnout cases underscores its significance in today's society. <!-- ref. needed -->
Despite extensive research, the exact causes and antecedents of burnout are not fully understood. <!-- ref. needed? --> 
This study investigates the relationship between burnout, its underlying mechanisms, and protective factors, extending previous research on factors mediating the role of cognitive motivation in burnout [@Grass-2018; @Zerna-2022] from aspiring and experienced teachers to healthcare professionals. 
The following section explains the mediation model and its variables.

## Theoretical Framework

...

## The present study

...

### Correlational Research Questions and Hypotheses
<!-- deliberate on whether/how we want to state the hypotheses; note that the results part aligns strongly to these hypotheses -->

RQ1: Is there a relationship between Need for Cognition (NFC), self-control, adaptive and maladaptive coping strategies, the emotion regulation strategies reappraisal and suppression, as well as the burnout dimension reduced personal efficiency (rPE)?

- H1a: There will be a moderate positive relationship between NFC and self-control.

- H1b: There will be a small positive relationship between NFC and reappraisal and no relationship between NFC and suppression.

- H1c: There will be a moderate positive relationship between NFC and adaptive coping and a small negative relationship between NFC and maladaptive coping.

- H1d: There will be a medium negative relationship between NFC and rPE.

- H1e: There will be a large negative relationship between self-control and rPE.

- H1f: There will be a medium negative relationship between reappraisal and rPE and a no relationship between suppression and rPE.

- H1g: There will be a large negative relationship between adaptive coping and rPE and a large positive relationship between maladaptive coping and rPE. 

RQ2: Is there a relationship between NFC, self-control, adaptive and maladaptive coping strategies, the emotion regulation strategies reappraisal and suppression, as well as the burnout dimension emotional exhaustion?

RQ3: Is there a relationship between NFC, self-control, adaptive and maladaptive coping strategies, the emotion regulation strategies reappraisal and suppression, as well as the burnout dimension depersonalization?

### Mediational Research Questions and Hypotheses

RQ4: To what extent do self-control, adaptive and maladaptive coping strategies, as well as the emotion regulation strategies reappraisal and suppression mediate the relationship between NFC and the burnout dimension rPE?

- H4a: The relationship between NFC and rPE will not be mediated by self-control. However, higher NFC will be associated with more self-control, whereby self-control will not be associated with rPE.

- H4b: The relationship between NFC and rPE will be partly mediated by reappraisal, whereby a higher NFC is associated with higher reappraisal, which, in turn is associated with lower rPE.

- H4c: The relationship between NFC and rPE will not be mediated by suppression.

- H4d: The relationship between NFC and rPE will be partly mediated by adaptive coping, whereby a higher NFC is associated with more adaptive coping, which, in turn is associated with lower rPE.

- H4e: The relationship between NFC and rPE will be partly mediated by maladaptive coping. A higher NFC is associated with less maladaptive coping, and, in turn, less maladaptive coping is associated with lower rPE.

RQ5: To what extent do self-control, adaptive and maladaptive coping strategies, as well as the emotion regulation strategies reappraisal and suppression mediate the relationship between NFC and the burnout dimensions emotional exhaustion?

RQ6: To what extent do self-control, adaptive and maladaptive coping strategies, as well as the emotion regulation strategies reappraisal and suppression mediate the relationship between NFC and the burnout dimensions depersonalization?

# Methods
We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study [cf. @Simmons-2012]. 

## Procedure
The study was preregistered at https://osf.io/d6y9k. Data were collected in two thesis projects [@Kadur-2018; @Ziessler-2019]. For the 2018 study (ref. V-259-15-AS-NFC-28032018), the Ethics Committee of Chemnitz University of Technology waived a full review; the 2019 study (ref. V-336-15-AS-Ressourcen-16052019) received approval without concerns. Participants (age $\ge$ 18 years, German-speaking, employed in healthcare) were recruited via clinics, care facilities, and universities  across the German dederal states of Saxony and Hesse as well as via social media and personal contacts. Data were gathered anonymously through online Enterprise Feedback Suite Survey platform (EFS,  [@Questback-2017]). A control item checked response sincerity. Participants received study information, gave informed consent, and could enter a raffle (€25 per 100 participants), request study results, and obtain information on burnout risk factors. Emails for the raffle were stored separately from survey data.

## Participants

```{r sample, echo = FALSE, warning = F}
preprocessed_data <- readRDS(here("Data", "NFC-Caregiver_DataAnalysis.RDS"))
data <- load(here("Data", "NFC-Caregiver_Data.Rdata"))

profession <- function(label = 1) { 
  return(printnum(length(which(unclass(data_ZK$profession) == label))/nrow(data_ZK)*100, digits = 1))
  }
```
<!-- -->
After the exclusion of participants because of incorrect scale labeling, missing consent to be interviewed, double participation, not having answered the questions seriously, not working in a healthcare profession or not being educated to do so, or having taken less than the average time to complete the questionnaires (see pregistration https://osf.io/d6y9k, section Data exclusion for details), the usable subsamples comprised $n_{2018}=431$, and $n_{2019}=229$ participants<!-- can these figures be found somewhere in the raw or preprocessed data? -->. The resulting total sample therefore consisted of $N=$ `r nrow(data_ZK)` (`r paste(table(unclass(data_ZK$sex)), c("female", "male", "diverse"), collapse = ", ")`; age range `r paste(range(data_ZK$age), collapse = " to ")` years, $M=$ `r printnum(mean(data_ZK$age), digits = 1)`, $SD=$ `r printnum(sd(data_ZK$age), digits = 1)` years). 
The majority of participants worked as nurses (`r profession(1)`%), while `r profession(5)`% held management positions in healthcare. 
Others were employed as social workers (`r profession(4)`%), psychotherapists (`r profession(3)`%), and other therapeutic professions such as occupational therapist or healthcare volunteers. 
Detailed demographic data are provided in Supplementary Table S1. <!-- create Table S1 -->
In both studies, the sample sizes were constrained by the number of participants that could be recruited during the limited timeframe of the respective thesis projects. A post-hoc power analysis ($t-$test, linear multiple regression, fixed model, single regression coefficient) was conducted using G\*Power [@Faul-2007]. The smallest standardized indirect effect from the mediation analysis in Grass et al. (2018) was $|\beta|=.05$, yieling $f^2=\beta/(1-\beta)=.05$. With a sample size of $N=642$, we achieved a power of >.99 to detect such an effect at $\alpha<.05$. <!-- analysis with G\*Power as in preregistration, but via simulations would perhaps be more suitable? --> 

## Material

```{r reliabilities, echo = FALSE, warning = F}
# function for determining McDonald's omega and Cronbach's alpha
ao <- function(df) {
  options( warn = -1 )
  o = print_num(psych::omega(df, plot = F)$omega.tot, gt1 = F)
  a = print_num(psych::alpha(df)$total$raw_alpha, gt1 = F)
  return(paste0(o, " (", a, ")"))
}

# following code needed ???
rel_mbi = ao(as.matrix(preprocessed_data[grep("mbi", colnames(preprocessed_data))]))

# calculate MacDonald's omega and Cronbach's alpha for all scales
scales = c("mbi", "mbi_rpe", "mbi_ee", "mbi_de", "nfc", "sc", "ers_[re|su]", "ers_re", "ers_su", "adapt_", "^adapt_", "^maladapt_")
alphas = omegas = NULL

for (i in 1:length(scales)) {
  omg=omega(preprocessed_data[grep(scales[i], colnames(preprocessed_data))], plot = F)
  alphas = c(alphas, omg$alpha)
  omegas = c(omegas, omg$omega.tot)
}

rel = data.frame(a=alphas, o=omegas)
rownames(rel) = scales

```
All questionnaires used were administered in German language. 
The reliabilities (MacDonald’s $\omega$ and Cronbach's $\alpha$) of the inventories used can be found in Table 1.
The burnout dimensions *reduced personal efficiency*, *emotional exhaustion*, and *depersonalization* were assessed using the German version of the 22-item Maslach Burnout Inventory [MBI-D, @Buessing-1992]. 
Items such as “I feel burned out by my job.” were rated on a scale from 1 (does not occur at all) to 6 (occurs very often/strongly). 
The internal consistencies of the MBI-D subscales showed good to excellent reliabilities, MacDonald's $\omega\ge$ = `r printnum(min(rel$o[1:4]), gt1 = F)`.

NFC was assessed with the 16-item short version of the German NFC scale [NCS, @Bless-1994] with items like “I like it when my life is full of tricky tasks that I have to solve.” These items were rated on a seven-point rating scale ranging from +3 (very accurate) to –3 (completely inaccurate). 
The scale demonstrated an excellent internal consistency of MacDonald’s $\omega=$ `r printnum(rel$o[which(rownames(rel)=="nfc")], gt1 = F)`. 

Self-control was measured by the 13-item short form of the Self-Control Scale [SCS-K-D, @Bertrams-2009]. 
Here, a five-point Likert scale from 1 (completely inaccurate) to 5 (completely accurate) was used to answer questions like "I am good at resisting temptations."
This scale showed an acceptable internal consistency of MacDonald’s $\omega=$ `r printnum(rel$o[which(rownames(rel)=="sc")], gt1 = F)`.

Further, the Emotion Regulation Questionnaire [ERQ-D, @Abler-2009], which included 10 items, was used to assess reappraisal and suppression. Reappraisal was measured by items like "When I get into a stressful situation, I change my thoughts about the situation, so it calms me down." 
Suppression was determined by items such as "I keep my feelings to myself." 
Participants responded on a scale ranging from 1 (not true at all) to 7 (absolutely true).
The six-item reappraisal subscale and the four-item suppression subscale showed good reliability with MacDonald’s $\omega\ge$ `r printnum(min(rel$o[which(rownames(rel) == "ers_re" | rownames(rel) == "ers_su")]), gt1 = F)`.

Finally (and differing from the material used by @Grass-2018), the 20-item Stress and Coping Inventory [SCI, @Satow-2012] was used to measure adaptive and maladaptive coping strategies on a scale ranging from 1 (does not apply) to 4 (applies exactly).
Adaptive coping was assessed by the subscales “positive thinking”, “active stress management”, “social support”, and “holding on to faith”. 
These subscales, consisting of 16 items such as "When stress and pressure arise, I directly address the causes," altogether demonstrated a good  internal consistency, MacDonald’s Omega $\omega=$ `r printnum(min(rel$o[which(rownames(rel) == "^adapt_")]), gt1 = F)`. 
Maladaptive coping was measured with the “increased alcohol and cigarette consumption” subscale, containing four items like "When I am under too much stress, I smoke a cigarette." 
This subscale had a questionable internal consistency of MacDonald’s $\omega=$ `r printnum(min(rel$o[which(rownames(rel) == "^maladapt_")]), gt1 = F)`.

## Statistical analyses
We used `r cite_r("r-references.bib")` for our analyses.

```{r normality, echo = F} 

# retain only variables of interest (MBI subscales, NFC, Self-Control, emotion regulation strategies, and coping styles) 
df_analysis = score_ZK[, c("mbi_ee", "mbi_rpe", "mbi_de", "nfc", "scs", "erq_reap", "erq_supp", "sci_adapt", "sci_maladapt")]

# tests for univariate and multivariate normality

# summary function for Shapiro-Wilk tests on univariate normality 
sw <- function(x) {
  x = data.frame(x)
  d = dim(x)
  n = names(x)
  r = NULL
  for (i in 1:dim(x)[2]) {
    y = shapiro.test(x[,i])
    v = cbind(y$statistic,y$p.value)
    colnames(v) = c("W","p")
    rownames(v) = n[i]
    r = rbind(r,v)
    }
  return(round(r,3))
}

# results of tests for univariate and multivariate normality
uvn = sw(df_analysis)
mvn = mardia(df_analysis, plot=F)

# report Spearman correlations with 95% CI and p-value 
report_cor <- function(x1, x2) {
  ct = corr.test(x1, x2, method = "spearman")
  if (ct$p < .001) { p = "< .001" } else { p = paste0("= ", print_p(ct$p)) }
  result = paste0('$r_{s}=$ ', printnum(ct$ci['r'], gt1=F), ', 95% CI [', printnum(ct$ci['lower'], gt1=F), ', ', printnum(ct$ci['upper'], gt1=F), '], $p$ ', p)
  return(result)
}

# classify correlations according to Gignac & Szodorai (2016)
classify_r <- function(x1, x2) {
  r = as.numeric(corr.test(x1, x2, method = "spearman")$ci['r'])
  if (r > 0) {direction = "positive"} else {direction = "negative"}
  if (is.na(r)) {
    return(NA)
  } else if (abs(r) >= 0.3) {
    return(paste("a large", direction))
  } else if (abs(r) >= 0.2) {
    return(paste("a medium", direction))
  } else if (abs(r) >= 0.1) {
    return(paste("a small", direction))
  } else {
    return("no")
  }
}

```
Robust tests were used to account for deviation from univariate and multivariate normality of the study variables, i.e. the MBI subscales, NFC, self-control, emotion regulation strategies, and coping styles; Shapiro-Wilk and Mardia tests, all $p\ge.001$). Spearman correlations were calculated to address the research questions (RQ) regarding bivariate relationships between Need for Cognition (NFC), self-control, adaptive and maladaptive coping strategies, the emotion regulation strategies reappraisal and suppression with the burnout dimensions *reduced personal efficiency* (rPE; RQ1), *emotional exhaustion* (EE; RQ2), and *depersonalization* (DE; RQ3). Statistical significance was evaluated based on the correlations' 95% CI not including zero, which with our sample size was the case for all $|r_{s}|\ge.077$. Effect size classification followed empirically derived thresholds [@Gignac-2016], i.e., $r_{s} \ge$ .10, .20, and .30 for small, medium, and large correlations. To address the research questions on possible mediation effects, i.e., whether self-control, reappraisal and suppression, and adaptive and maladaptive coping mediate the relationship between NFC and the burnout dimensions rPE (RQ4), EE (RQ5), and DE (RQ6), multiple mediation models were tested using *lavaan* with robust Maximum Likelihood estimation of standard errors.

# Results

```{r RQ1-3, echo = F, warning = F}


# prepare reliabilities for Table 1 diagonal
print_rel = print_num(rel, gt1 = F)
rel_diag = paste0(print_rel$o, " (", print_rel$a, ")")

# correlations
ct_ZK=corr.test(score_ZK[ , c(11,13,12,14:22)], method = "spearman", adjust = "none")
ct = print_num(ct_ZK$r, gt1 = F)
ct[upper.tri(ct)] = ""
diag(ct) = rel_diag
rownames(ct) = c("1. MBI", "2. MBI RPE", "3. MBI EE", "4. MBI DE", "5. NFC", "6. SCS", "7. ERQ", "8. ERQ R", "9. ERQ S", "10. SCI", "11. SCI A", "12. SCI MA")
colnames(ct) = paste(1:12)

# descriptives
dt = t(print_num(describe(score_ZK[ , c(11,13,12,14:22)])[, c(3:4, 8, 9, 11, 12)]))
rownames(dt) = c("Mean", "SD", "Min", "Max", "Skew", "Kurtosis")
colnames(dt) = paste(1:12)

apa_table(list(ct, dt), landscape = T, midrules = 12, format.args = list(gt1 = F), align = c("l",rep("r", 12)), font_size = "scriptsize",
          caption = "Spearman correlations and internal consistencies of the questionnaire scores (outliers included)",
          note = "\\textit{N} = 642. The 95\\% CI does not include zero for $|r_{s}|\\geq$ .077. The diagonal provides MacDonald’s $\\omega$ and Cronbach’s $\\alpha$ (in brackets). MBI = Maslach Burnout Inventory; MBI RPE = Reduced Personal efficiency subscale; MBI EE = Emotional Exhaustion subscale; MBI DE = Depersonalisation subscale; NFC = Need for Cognition Scale; SCS = Self Control Scale; ERQ = Emotion Regulation Questionnaire; ERQ R = Reappraisal subscale; ERQ S = Suppression subscale; SCI = Stress and Coping Inventory; SCI A = Adaptive coping subscales; SCI MA = Maladaptive coping subscale",
          escape = F)
```

Table 1 shows bivariate Spearman correlations between the study variables. Results for research questions 1–3 are summarized below.

### Research Question 1  
We examined links between Need for Cognition (NFC), self-control, the habitual use of the emotion strategies reappraisal and suppression, coping strategies, and *reduced personal efficiency*. We observed `r classify_r(df_analysis$nfc, df_analysis$scs)` correlation between NFC and self-control, `r report_cor(df_analysis$nfc, df_analysis$scs)` (H1a), but no correlation with reappraisal, `r report_cor(df_analysis$nfc, df_analysis$erq_reap)`, or suppression, `r report_cor(df_analysis$nfc, df_analysis$erq_supp)` (H1b). NFC showed `r classify_r(df_analysis$nfc, df_analysis$sci_a)` correlation with adaptive coping, `r report_cor(df_analysis$nfc, df_analysis$sci_a)`, and `r classify_r(df_analysis$nfc, df_analysis$sci_ma)` correlation with maladaptive coping, `r report_cor(df_analysis$nfc, df_analysis$sci_ma)` (H1c). *Reduced personal efficiency* correlated with NFC, `r report_cor(df_analysis$nfc, df_analysis$mbi_rpe)`, i.e. `r classify_r(df_analysis$nfc, df_analysis$mbi_rpe)` effect (H1d), self-control, `r report_cor(df_analysis$mbi_rpe, df_analysis$scs)`, i.e. `r classify_r(df_analysis$scs, df_analysis$mbi_rpe)` effect (H1e), reappraisal and suppression, `r report_cor(df_analysis$mbi_rpe, df_analysis$erq_reap)`, i.e. `r classify_r(df_analysis$erq_reap, df_analysis$mbi_rpe)` effect, and `r report_cor(df_analysis$mbi_rpe, df_analysis$erq_supp)`, i.e. `r classify_r(df_analysis$erq_supp, df_analysis$mbi_rpe)` effect (H1f), as well as adaptive and maladaptive coping, `r report_cor(df_analysis$mbi_rpe, df_analysis$sci_a)`, i.e. `r classify_r(df_analysis$sci_a, df_analysis$mbi_rpe)` effect, and `r report_cor(df_analysis$mbi_rpe, df_analysis$sci_ma)`, i.e. `r classify_r(df_analysis$sci_ma, df_analysis$mbi_rpe)` effect (H1g).

### Research Question 2  
*Emotional exhaustion* correlated with all variables: NFC, `r report_cor(df_analysis$mbi_ee, df_analysis$nfc)`, self-control, `r report_cor(df_analysis$mbi_ee, df_analysis$scs)`, reappraisal, `r report_cor(df_analysis$mbi_ee, df_analysis$erq_reap)`, and suppression, `r report_cor(df_analysis$mbi_ee, df_analysis$erq_supp)`, and both coping strategies, `r report_cor(df_analysis$mbi_ee, df_analysis$sci_a)`, and `r report_cor(df_analysis$mbi_ee, df_analysis$sci_ma)`.  

### Research Question 3  
For *depersonalization*, no correlations emerged for NFC, `r report_cor(df_analysis$mbi_de, df_analysis$nfc)`, or self-control, `r report_cor(df_analysis$mbi_de, df_analysis$scs)`, but significant ones appeared for reappraisal, `r report_cor(df_analysis$mbi_de, df_analysis$erq_reap)`, suppression, `r report_cor(df_analysis$mbi_de, df_analysis$erq_supp)`, as well as for both coping strategies, `r report_cor(df_analysis$mbi_de, df_analysis$sci_a)`, and `r report_cor(df_analysis$mbi_de, df_analysis$sci_ma)`.  

Figures 1–3 summarize the mediation analyses (research questions 4–6). Only standardized coefficients and $p$-values are reported for ease of reading; full statistics appear in Tables 2–4. 

```{r mediation, echo = F, warning = F}
model_mbi = "
  # direct effect
    mbi ~ c*nfc
  # mediators
    scs ~ a1*nfc
    erq_reap ~ a2*nfc
    erq_supp ~ a3*nfc
    sci_adapt ~ a4*nfc
    sci_maladapt ~ a5*nfc
    mbi ~ b1*scs + b2*erq_reap + b3*erq_supp + b4*sci_adapt + b5*sci_maladapt
  # indirect effects 
    ind1 := a1*b1
    ind2 := a2*b2
    ind3 := a3*b3
    ind4 := a4*b4
    ind5 := a5*b5
  # total effect
    total := ind1 + ind2 + ind3 + ind4 + ind5 + c
"

# specify rownames for data.frame
rownames_df = c(
  "\\textit{Direct effect of NFC on MBI}",
  "a1: Self-Control",
  "a2: Reappraisal",
  "a3: Suppression",
  "a4: Adaptive Coping",
  "a5: Maladaptive Coping",
  "b1: Self-Control",
  "b2: Reappraisal",
  "b3: Suppression",
  "b4: Adaptive Coping",
  "b5: Maladaptive Coping",
  "ind1: Self-Control",
  "ind2: Reappraisal",
  "ind3: Suppression",
  "ind4: Adaptive Coping",
  "ind5: Maladaptive Coping",
  "\\textit{Total effect}"
)

report_pe <-  function(fit, label=NULL, txt = F, beta_only = F) {
  pe=parameterEstimates(fit, standardized = T)[,c("label", "est", "se", "ci.lower", "ci.upper", "pvalue", "std.all")]
  if (is.null(label)) {
    result = pe
  } else {
    result = pe[which(pe[,1]==label),]
  }
  if (txt == T & length(label) == 1) {
    if (result$pvalue < .001) { p = " < .001" } else { p = paste0(" = ", printp(result$pvalue)) }
    if (beta_only == F) {
    result = paste0("$B=$ ", printnum(result$est, gt1=T), ", $SE=$ ", printnum(result$se, gt1=T), ", 95% CI [", printnum(result$ci.lower, gt1=T), ", ", printnum(result$ci.upper, gt1=T), "], $p$ ", p, ", $\\beta=$ ", printnum(result$std.all, gt1 = F))
    } else {
    result = paste0("$\\beta=$ ", printnum(result$std.all, gt1 = F), ", $p$", p)  
    }
  }
  return(result)
}
```


```{r RQ4, echo = F, warning = F}
# specify model for reduced personal efficiency (rpe)
model_rpe = gsub("mbi", "mbi_rpe", model_mbi)

# fit rpe model
fit_rpe=sem(model_rpe, df_analysis, estimator="MLR")

# create table with parameter estimates
pe_rpe = parameterEstimates(fit_rpe, standardized = T)
pe_rpe_table=printnum(pe_rpe[c(1:11,19:24),c("est","se","ci.lower", "ci.upper", "pvalue", "std.all")], digits = 3)

# create data.frame for table
df <- pe_rpe_table

colnames(df) <- c("B","SE","CI.lower","CI.upper","p","beta")
df$beta = sub("0.", ".", df$beta)

rownames(df) <- gsub("MBI", "rPE", rownames_df)

df <- df %>%
  mutate(
    p = ifelse(p == 0 | p == .000, "< .001",
               ifelse(p < .001, "< .001",
                      sub("^0\\.", ".", formatC(p, digits = 3, format = "f"))))
  )

colnames(df) = c("$B$", "$SE$", "$LB$", "$UB$", "$p$", "$\\beta$")
apa_table(
  df,
  escape = F, align = c("l", rep("r",6)), font_size = "footnotesize", 
  stub_indents = list(`\\textit{NFC to Mediators}` = 2:6,
                      `\\textit{Mediators to rPE}` = 7:11,
                      `\\textit{Indirect effects}` = 12:16),
  midrules = c(1,7,13,19), 
  caption = "Mediation of the effect of Need for Cognition (NFC) on reduced personal efficiency (rPE)",
  note = "$N=642$. $B$ = unstandardized coefficient, $SE$ = standard error of $B$, $LB/UB$ = lower and upper bound of the 95\\% confidence interval, $p$ = $p$-value, $\\beta$ = standardized coefficient, a = paths from predictor to mediator, b = paths from mediator to outcome, ind = indirect effects a*b."
)
```

### Research Question 4
Figure 1 and Table 2 present the results of the multiple mediation analysis for *reduced personal efficiency*. Roughly half of the total effect, `r report_pe(fit_rpe, 'total', txt = T, beta_only = T)`, stemmed from the direct path of NFC on reduced personal efficiency, `r report_pe(fit_rpe, 'c', txt = T, beta_only = T)`. While NFC predicted self-control, `r report_pe(fit_rpe, 'a1', txt = T, beta_only = T)`, self-control did not predict reduced personal efficiency, `r report_pe(fit_rpe, 'b1', txt = T, beta_only = T)`, hence, no mediation occured, `r report_pe(fit_rpe, 'ind1', txt = T, beta_only = T)` (H4a). Reappraisal partly mediated the NFC–efficiency link, `r report_pe(fit_rpe, 'ind2', txt = T, beta_only = T)` (H4b), while suppression did not, `r report_pe(fit_rpe, 'ind3', txt = T, beta_only = T)` (H4c). Adaptive coping mediated the effect of NFC on reduced personal efficiency, , `r report_pe(fit_rpe, 'ind4', txt = T, beta_only = T)` (H4d). Although NFC predicted maladaptive coping, `r report_pe(fit_rpe, 'a5', txt = T, beta_only = T)`, a mediation effect of maladaptive coping was not supported, , `r report_pe(fit_rpe, 'ind5', txt = T, beta_only = T)` (H4e).

![Multiple mediation of the relationship between Need for Cognition with the burnout dimension reduced personal efficiency. Standardized coefficients are given (bold: $p<.05$). Indirect paths are provided above the mediators, the remaining direct effect is given at the bottom of the figure together with the total effect (in brackets).](NFC-Caregiver_figures/Fig1.eps)

```{r RQ5, echo = F, warning = F}
# specify model for emotional exhaustion (ee)
model_ee = gsub("mbi", "mbi_ee", model_mbi)

# fit ee model
fit_ee=sem(model_ee, df_analysis, estimator="MLR")

# create table with parameter estimates
pe_ee = parameterEstimates(fit_ee, standardized = T)
pe_ee_table=printnum(pe_ee[c(1:11,19:24),c("est","se","ci.lower", "ci.upper", "pvalue", "std.all")], digits = 3)

# create data.frame for table
df <- pe_ee_table

colnames(df) <- c("B","SE","CI.lower","CI.upper","p","beta")
df$beta = sub("0.", ".", df$beta)

rownames(df) <- gsub("MBI", "EE", rownames_df)

df <- df %>%
  mutate(
    p = ifelse(p == 0 | p == .000, "< .001",
               ifelse(p < .001, "< .001",
                      sub("^0\\.", ".", formatC(p, digits = 3, format = "f"))))
  )

colnames(df) = c("$B$", "$SE$", "$LB$", "$UB$", "$p$", "$\\beta$")
apa_table(
  df,
  escape = F, align = c("l", rep("r",6)), font_size = "footnotesize", 
  stub_indents = list(`\\textit{NFC to Mediators}` = 2:6,
                      `\\textit{Mediators to EE}` = 7:11,
                      `\\textit{Indirect effects}` = 12:16),
  midrules = c(1,7,13,19), 
  caption = "Mediation of the effect of Need for Cognition (NFC) on emotional exhaustion (EE)",
  note = "$N=642$. $B$ = unstandardized coefficient, $SE$ = standard error of $B$, $LB/UB$ = lower and upper bound of the 95\\% confidence interval, $p$ = $p$-value, $\\beta$ = standardized coefficient, a = paths from predictor to mediator, b = paths from mediator to outcome, ind = indirect effects a*b."
)
```

### Research Question 5  
Figure 2 and Table 3 show the model for *emotional exhaustion*. Less than half of the total effect, `r report_pe(fit_ee, 'total', txt = T, beta_only = T)`, was due to the direct path, `r report_pe(fit_ee, 'c', txt = T, beta_only = T)`. Mediation occurred for adaptive coping, `r report_pe(fit_ee, 'ind4', txt = T, beta_only = T)`, and maladaptive coping, `r report_pe(fit_ee, 'ind5', txt = T, beta_only = T)`, but not for self-control, `r report_pe(fit_ee, 'ind1', txt = T, beta_only = T)`, reappraisal, `r report_pe(fit_ee, 'ind2', txt = T, beta_only = T)`, or suppression, `r report_pe(fit_ee, 'ind3', txt = T, beta_only = T)`.

![Multiple mediation of the relationship between Need for Cognition with the burnout dimension emotional exhaustion. Standardized coefficients are given (bold: $p< .05$). Indirect paths are provided above the mediators, the remaining direct effect is given at the bottom of the figure together with the total effect (in brackets).](NFC-Caregiver_figures/Fig2.eps)

```{r RQ6, echo = F, warning = F}
# specify model for depersonalization (de)
model_de = gsub("mbi", "mbi_de", model_mbi)

# fit de model
fit_de=sem(model_de, df_analysis, estimator="MLR")

# create table with parameter estimates
pe_de = parameterEstimates(fit_de, standardized = T)
pe_de_table=printnum(pe_de[c(1:11,19:24),c("est","se","ci.lower", "ci.upper", "pvalue", "std.all")], digits = 3)

# create data.frame for table
df <- pe_de_table

colnames(df) <- c("B","SE","CI.lower","CI.upper","p","beta")
df$beta = sub("0.", ".", df$beta)

rownames(df) <- gsub("MBI", "DE", rownames_df)

df <- df %>%
  mutate(
    p = ifelse(p == 0 | p == .000, "< .001",
               ifelse(p < .001, "< .001",
                      sub("^0\\.", ".", formatC(p, digits = 3, format = "f"))))
  )

colnames(df) = c("$B$", "$SE$", "$LB$", "$UB$", "$p$", "$\\beta$")
apa_table(
  df,
  escape = F, align = c("l", rep("r",6)), font_size = "footnotesize", 
  stub_indents = list(`\\textit{NFC to Mediators}` = 2:6,
                      `\\textit{Mediators to DE}` = 7:11,
                      `\\textit{Indirect effects}` = 12:16),
  midrules = c(1,7,13,19), 
  caption = "Mediation of the effect of Need for Cognition (NFC) on depersonalization (DE)",
  note = "$N=642$. $B$ = unstandardized coefficient, $SE$ = standard error of $B$, $LB/UB$ = lower and upper bound of the 95\\% confidence interval, $p$ = $p$-value, $\\beta$ = standardized coefficient, a = paths from predictor to mediator, b = paths from mediator to outcome, ind = indirect effects a*b."
)
```

### Research Question 6  
Figure 3 and Table 4 show the model for *depersonalization*. About one third of the total effect, `r report_pe(fit_de, 'total', txt = T, beta_only = T)`, reflected the direct path, `r report_pe(fit_de, 'c', txt = T, beta_only = T)`. Again, mediation was found for adaptive and maladaptive coping, `r report_pe(fit_de, 'ind4', txt = T, beta_only = T)`, and `r report_pe(fit_de, 'ind5', txt = T, beta_only = T)`, but not for self-control, `r report_pe(fit_de, 'ind1', txt = T, beta_only = T)`, reappraisal, `r report_pe(fit_de, 'ind2', txt = T, beta_only = T)`, or suppression, `r report_pe(fit_de, 'ind3', txt = T, beta_only = T)`.  

![Multiple mediation of the relationship between Need for Cognition with the burnout dimension depersonalization. Standardized coefficients are given (bold: $p< .05$). Indirect paths are provided above the mediators, the remaining direct effect is given at the bottom of the figure together with the total effect (in brackets).](NFC-Caregiver_figures/Fig3.eps)

```{r save_image, echo = F, warning = F}
save.image(here("Data", "NFC-Caregiver_RMarkdown-generated.RData"))
```


# Discussion
<!--
Summary/Evaluation by **ChatGPT**:

(1) Check of hypotheses vs. results
H1a (NFC - self-control, moderate positive)
Result: large positive correlation (rs = .56).
**!!!** Hypothesis supported, but effect size larger than predicted.
H1b (NFC - reappraisal small positive; no link with suppression)
Result: no correlation with reappraisal, none with suppression.
**XXX** Hypothesis not supported (expected small positive with reappraisal).
H1c (NFC - adaptive coping moderate positive; maladaptive coping small negative)
Result: small positive with adaptive (rs = .15); large negative with maladaptive (rs = –.30).
**X!X** Partially supported (direction correct, effect sizes differ).
H1d (NFC - rPE medium negative)
Result: small negative (rs = –.19).
**XXX**Not supported (effect weaker than predicted).
H1e (self-control - rPE large negative)
Result: small negative (rs = –.18).
**XXX** Not supported (weaker effect).
H1f (reappraisal - rPE medium negative; suppression - no link)
Result: reappraisal medium negative (rs = –.29), suppression small positive (rs = .12).
**X!X**Reappraisal part supported; suppression contradicts prediction.
H1g (adaptive coping - rPE large negative; maladaptive coping - large positive)
Result: adaptive coping large negative (rs = –.42, **!!!** supported); maladaptive small positive (rs = .11, **XXX** weaker than predicted).
RQ2 (Emotional exhaustion)
Result: significant correlations with all predictors in expected directions (NFC, self-control, reappraisal negative; suppression, maladaptive coping positive; adaptive coping negative).
**!!!** Clear pattern, although effect sizes modest.
RQ3 (Depersonalization)
Result: NFC and self-control not significant; reappraisal (–), suppression (+), adaptive coping (–), maladaptive coping (+).
**!!!** Clear, but partly divergent from RQ1–2: NFC/self-control play no role here.
H4a (Mediation via self-control not supported)
Result: confirmed.
H4b (Mediation via reappraisal partial)
Result: small significant mediation (beta = –.01, p = .049).
**!!!** Supported.
H4c (Suppression mediation absent)
Result: confirmed.
H4d (Mediation via adaptive coping partial)
Result: significant mediation (beta = –.07).
**!!!** Supported.
H4e (Mediation via maladaptive coping partial)
Result: no mediation (beta = .00).
**XXX** Not supported.
RQ5 (Mediation on emotional exhaustion)
Result: only adaptive and maladaptive coping mediated.
RQ6 (Mediation on depersonalization)
Result: only adaptive and maladaptive coping mediated.
(2) Draft Summary for Discussion Intro
-->

## Summary of Findings
The present study examined the role of Need for Cognition (NFC), self-control, coping, and emotion regulation strategies in predicting burnout dimensions in healthcare professionals. Overall, results partly supported the proposed hypotheses. NFC was strongly associated with self-control and showed beneficial links with adaptive coping and lower maladaptive coping, although effect sizes did not always align with expectations. Contrary to predictions, NFC was unrelated to reappraisal and suppression, and its associations with burnout were weaker than hypothesized.

Regarding burnout dimensions, NFC, self-control, and reappraisal were negatively related to reduced personal efficiency and emotional exhaustion, whereas suppression and maladaptive coping were positively related. For depersonalization, however, NFC and self-control showed no significant associations, suggesting limited relevance of these factors for this burnout facet.

Mediation analyses revealed that adaptive coping consistently accounted for part of the protective role of NFC across all burnout dimensions, while maladaptive coping mediated the effects of NFC on emotional exhaustion and depersonalization, but not on reduced personal efficiency. By contrast, self-control did not function as a mediator, and only a minor indirect effect emerged via reappraisal.

## Evaluation of Hypotheses

Supported: H1a, H1f (reappraisal part), H1g (adaptive coping), H4a, H4b, H4c, H4d.

Partially supported: H1c, H1f (suppression part).

Not supported: H1b, H1d, H1e, H1g (maladaptive coping), H4e.

Together, these findings highlight the central importance of coping strategies, particularly adaptive coping, in linking cognitive-motivational resources such as NFC to burnout outcomes, while emotion regulation strategies and self-control played a more limited role.

\newpage
  
# References

::: {#refs custom-style="Bibliography"}
:::
